Appendix 3: Example of a spatially varying effect of climate on citizen science count data with sdmTMB

### 2021-12-22 doc/appendix-snow-sdmTMB.Rmd
Edit snowy app.

```{r load-models, warning=FALSE, message=FALSE, echo=FALSE, cache=FALSE}
m0 <- readRDS(here::here("data/snow_w_main_effect_0_150km.rds"))
m1 <- readRDS(here::here("data/snow_w_main_effect_1_150km.rds"))
m2 <- readRDS(here::here("data/snow_w_main_effect_150km.rds"))
```

@@

The `nbinom2` distribution appears to have the best fit. 
We will rerun with `reml = TRUE` to ensure better estimation of the random effects that dominate this model.

@@

Print the model to inspect the fit:
```{r check, include = FALSE, cache=FALSE, eval=TRUE}
m <- readRDS(here::here("data/snow_w_main_effect_150km_reml.rds"))
m # loading this twice just prevents some excess messages from cluttering the output when printing below
```

@@

View the confidence intervals on both fixed and random parameter estimates using `tidy()`.

@@

<!-- \clearpage -->
Check the spatiotemporal distribution of the residuals.

@@

<!-- \clearpage -->

>>>>

```{r load-models, warning=FALSE, message=FALSE, echo=FALSE, cache=FALSE}
if (rds_saved) {
  m0 <- readRDS(here::here("data/snow_w_main_effect_0_150km.rds"))
  m1 <- readRDS(here::here("data/snow_w_main_effect_1_150km.rds"))
  m2 <- readRDS(here::here("data/snow_w_main_effect_150km.rds"))
}
```

@@

According to AIC, the `nbinom2()` (negative binomial, NB2) distribution appears to have the most parsimonious fit. 
We will rerun with `reml = TRUE` to ensure better estimation of the random effects that dominate this model.

@@

Print the model to inspect the fit:

```{r check, include = FALSE, cache=FALSE, eval=TRUE}
if (rds_saved2) {
  m <- readRDS(here::here("data/snow_w_main_effect_150km_reml.rds"))
}
# m # loading this twice just prevents some excess messages from cluttering the output when printing below
```

@@

View the confidence intervals on both fixed and random (and variance) parameter estimates using `tidy()`.

@@

Check the spatiotemporal distribution of the residuals.

@@
